---
title: "R_Assignment"
author: "Eric"
date: "2025-10-12"
output:
  html_document: default
  pdf_document: default
---
trace() and recover() are used for debugging in R.

Trace() allows you to get inside a function and add a message or action, such as displaying the inputs, without affecting the original code. 

 When an error occurs, you can use recover() to figure out what went wrong.  It pauses the application and displays a list of the stages that resulted in the problem, allowing you to hop in and examine the values at each step.

```{r}
# A simple function that multiplies two numbers
multiply_values <- function(num1, num2) {
  product <- num1 * num2
  return(product)
}

# Use trace() to print inputs when multiply_values() is called
trace("multiply_values", tracer = quote(cat("Tracing: num1 =", num1, "num2 =", num2, "\n")))

# Call the function to see trace output
multiply_values(4, 7)

# Remove the trace after testing
untrace("multiply_values")


```


```{r, error=TRUE}
# Enable recover() to inspect errors interactively
options(error = recover)

# Function that performs subtraction
subtract_values <- function(a, b) {
  result <- a - b
  return(result)
}

# Function that uses subtract_values() and causes an error
compute_difference <- function(x) {
  y <- x * 2
  z <- subtract_values(y, "five")   # Error: cannot subtract a character
  return(z)
}

# Call the function to trigger recover()
compute_difference(8)

```

